### 2013-03-28 doc/sosp13/evaluation.tex
uts plot
uts story todo
Added profile table

\begin{figure}[ht]
    \begin{center}
%      \includegraphics[width=0.5\textwidth]{figs/grappa-uts.pdf}
    \end{center}
    \caption{Vertices per second in UTS on \Grappa as the number of nodes grows.}
    \label{fig:grappa-uts}
\end{figure}

@@

@@

\subsection{Application Results}
To evaluate \Grappa's performance with respect to the XMT, we ran each
of our three benchmarks on up to 16 nodes of each machine. \Grappa used
6 cores per node, with the best parameters chosen for each point. In
some cases, the XMT could not run the benchmark with 2 nodes, so the
point is omitted. \TODO{rewrite this!}
\subsubsection{Unbalanced Tree Search}\TODO{rewrite with new results}
%% UTS: performance comparison
\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{figs/uts_performance.pdf}
    \end{center}
    \caption{Performance of in-memory unbalanced tree search.}
    \label{fig:uts_compare}
\end{figure}

>>>>

\begin{figure}[ht]
    \begin{center}
%      \includegraphics[width=0.5\textwidth]{figs/grappa-uts.pdf}
    \end{center}
    \caption{Vertices per second in UTS on \Grappa as the number of nodes grows.}
    \label{fig:grappa-uts}
\end{figure}
\TODO{UTS: story here is T1 class is bushy trees similar to properties
    of real world networks. Larger T1XXL (4.5 B vertices) provides
    more parallelism for continued scaling up. T3 class is deep skinny
    trees. Grappa can do no better than the straightforward UPC impl: there very little
    parallelism and the critical path is long}

@@

\begin{figure}[ht]
    \begin{center}
      \begin{tabular}{c|c c c c}
        Benchmark     & Communication & User & Idle & Context Switch \\ \hline
        GUPS          & 6.60  & 42.94   & 47.74 & 2.80 \\
        BFS           & 54.84 & 30.90   & 10.94 & 3.43 \\ 
        Intsort       & 34.28 & 42.00   & 21.31 & 2.47 \\ 
        UTS           & 40.57 & 56.52   &  1.21 & 1.73 \\
        Pagerank      & 76.79 & 20.71   &  0.06 & 2.50 \\
      \end{tabular}
    \end{center}
    \caption{\Grappa\ execution time profile, in percent.}
%bar chart, one set of bars per benchmark, one bar per system. runtime normalized to grappa.
    \label{fig:grappa-profile}
\end{figure}

@@

\subsection{Application Results}
To evaluate \Grappa's performance with respect to the XMT, we ran each
of our three benchmarks on up to 16 nodes of each machine. \Grappa used
6 cores per node, with the best parameters chosen for each point. In
some cases, the XMT could not run the benchmark with 2 nodes, so the
point is omitted. \TODO{rewrite this!}
\subsubsection{Unbalanced Tree Search}\TODO{rewrite with new results}
%% UTS: performance comparison
\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{figs/uts_scale.pdf}
    \end{center}
    \caption{Performance of in-memory unbalanced tree search.}
    \label{fig:uts_compare}
\end{figure}
